Categorizing the trajectory dynamics of replay

### 2019-07-16 Article.tex
Update on Overleaf.

\documentclass[times, twoside, watermark]{zHenriquesLab-StyleBioRxiv}
\usepackage{blindtext}

@@

\item Use Chapman-Kolmogorov to define prior in terms of previous time step's posterior and state transitions
$$
\begin{align*}
p(x_{k}, I_{k} \mid y_{1:k-1}) &= \sum_{I_{k-1}} \int p(x_{k}, x_{k-1}, I_{k}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k}, I_{k} \mid x_{k-1}, I_{k-1}, y_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k}, I_{k} \mid x_{k-1}, I_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1}) * Pr(I_{k} \mid I_{k-1}, x_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\end{align*}$$

where:
$p(x_{k-1}, I_{k-1} \mid y_{1:k-1})$ is the previous posterior,
$Pr(I_{k} \mid I_{k-1}, x_{k-1})$ is the discrete state transition, and $p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1})$ is the continuous state transition

\item Final Filter
$$
p(x_{k}, I_{k} \mid y_{1:k}) \propto p(y_{k} \mid x_{k}, I_{k}) * \sum_{I_{k-1}} \int p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1}) * Pr(I_{k} \mid I_{k-1}, x_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
$$
\end{enumerate}

@@

\item
$$
\begin{align*}
p(x_{k+1}, I_{k+1} \mid y_{1:k}) &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1}, x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1} \mid x_{k}, I_{k}, y_{1:k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1} \mid x_{k}, I_{k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1} \mid x_{k}, I_{k+1}, I_{k}) * Pr(I_{k+1} \mid I_{k}, x_{k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\end{align*}$$

>>>>

\documentclass[times, twoside, watermark]{zHenriquesLab-StyleBioRxiv}
\usepackage{blindtext}
\usepackage{amsmath}

@@

\item Use Chapman-Kolmogorov to define prior in terms of previous time step's posterior and state transitions
$$
\begin{align*}
p(x_{k}, I_{k} \mid y_{1:k-1}) &= \sum_{I_{k-1}} \int p(x_{k}, x_{k-1}, I_{k}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k}, I_{k} \mid x_{k-1}, I_{k-1}, y_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k}, I_{k} \mid x_{k-1}, I_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\\ &= \sum_{I_{k-1}} \int p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1}) * Pr(I_{k} \mid I_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
\end{align*}$$

where:
$p(x_{k-1}, I_{k-1} \mid y_{1:k-1})$ is the previous posterior,
$Pr(I_{k} \mid I_{k-1})$ is the discrete state transition, and $p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1})$ is the continuous state transition

\item Final Filter
$$
p(x_{k}, I_{k} \mid y_{1:k}) \propto p(y_{k} \mid x_{k}, I_{k}) * \sum_{I_{k-1}} \int p(x_{k} \mid x_{k-1}, I_{k}, I_{k-1}) * Pr(I_{k} \mid I_{k-1}) * p(x_{k-1}, I_{k-1} \mid y_{1:k-1}) * dx_{k-1}
$$
\end{enumerate}

@@

\item
$$
\begin{align*}
p(x_{k+1}, I_{k+1} \mid y_{1:k}) &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1}, x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1} \mid x_{k}, I_{k}, y_{1:k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1}, I_{k+1} \mid x_{k}, I_{k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\\ &= \sum_{I_{k}} \int p(x_{k+1} \mid x_{k}, I_{k+1}, I_{k}) * Pr(I_{k+1} \mid I_{k}) * p(x_{k}, I_{k} \mid y_{1:k}) * dx_{k}
\end{align*}$$
